FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-20 NewVersion/sections/RelatedWork.tex

\noindent {\bf C++ model.}
C++ supports a very flexible inheritance model.
C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
With virtual methods, dynamic dispatch is used and 
method lookup algorithm will find the most specific method definition. 
A contribution of our work is to provide a minimal formal model of
hierarchical dispatching, whereas C++ can be viewed as a real-world
implementation. There are several formalizations~\cite{Wasserrab2006,ramananandro2012mechanized,Ramalingam1997} in the literature modeling C++ various features and give us some inspiration, however, as far as we know, there is no any formal model that
captures this aspect of the C++ method dispatching model. Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected since they are used for ambiguity resolution.
\bruno{The discussion points out further differences. We need to refer
to that discussion here too.}\yanlin{added.}

>>>>

\noindent {\bf C++ model.}
C++ supports a very flexible inheritance model.
C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
With virtual methods, dynamic dispatch is used and 
method lookup algorithm will find the most specific method definition. 
A contribution of our work is to provide a minimal formal model of
hierarchical dispatching, whereas C++ can be viewed as a real-world
implementation. There are several
formalizations~\cite{Wasserrab2006,ramananandro2012mechanized,Ramalingam1997}
in the literature modeling various C++ features. However, as far as we know, there is no formal model that
captures this aspect of the C++ method dispatching model. Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected since they are used for ambiguity resolution.
\bruno{The discussion points out further differences. We need to refer
to that discussion here too.}\yanlin{added.}
